Algorithm explanation

### 2013-09-26 article/experiment.tex
Experiment
Fix reference

We implemented our proposed algorithm into \textsc{MoCHi} by two steps.  First,
we replace an existing theorem prover with our interpolating theorem
prover as a sub-routine for solving Horn clauses in dependent typing.
We used a method to obtain a common small interpolant across different
interpolating problems, while reducing a Horn clause problem into
interpolation \cite{conf/ppdp/UnnoK09}.  Second, we completely
replaced MoCHi's Horn solving algorithm with our algorithm.

@@

Finally, we showed some test cases that may occur in practical interpolation.

\[\begin{array}{r c}
\multirow{2}{*}{$\varphi_A$}
& ((x-y-1 \leq 0) \wedge (-x+y-2 \leq 0) \wedge (x+y-1 \leq 0) \wedge (-x-y-2 \leq 0)) \vee \\
& ((x-y-2 \leq 0) \wedge (-x+y-1 \leq 0) \wedge (x+y-2 \leq 0) \wedge (-x-y-1 \leq 0)) \\
\hline
\varphi_B : & (x=0 \wedge y=2) \vee (x=0 \wedge y=-2)
\end{array}\]
\[\begin{array}{l c}
\text{\textsc{Yint}} & (-x+17y-33 \leq 0) \wedge (x-17y-33 \leq 0) \\
\text{\textsc{CSIsat}} & ((-1 \leq (x + y) \vee (x + -y) \leq 1) \wedge (-1 \leq (x + -y) \vee (x + y) \leq 1))
\end{array}\]

\begin{figure}
\begin{center}
\includegraphics[scale=1]{figures/int1.eps}
\end{center}
\caption{Interpolation}
\end{figure}

\[\begin{array}{r c}
\multirow{2}{*}{$\varphi_A$}
& ((y+1=0) \wedge (x-1=0)) \vee ((y+1=0) \wedge (x+1=0)) \vee \\
& ((y-1=0) \wedge (x+1=0)) \vee ((y-1=0) \wedge (x-1=0)) \\
\hline
\multirow{2}{*}{$\varphi_B$}
& ((y+2 \leq 0) \wedge (x-2 \geq 0)) \vee ((y+2 \leq 0) \wedge (x+2 \leq 0)) \vee \\
& ((y-2 \geq 0) \wedge (x+2 \leq 0)) \vee ((y-2 \geq 0) \wedge (x-2 \geq 0))
\end{array}\]
\begin{tabular}{l c}
\textsc{Yint} & $(-2y-3 \leq 0) \wedge (2y-3 \leq 0)$
\end{tabular}

\begin{figure}
\begin{center}
\includegraphics[scale=1]{figures/int2.eps}
\quad
\includegraphics[scale=1]{figures/int3.eps}
\end{center}
\caption{Interpolation}
\end{figure}

@@

\[\begin{array}{r c}
\varphi_A & (x=1 \wedge y=1) \vee (x=0 \wedge y=0) \\
\hline
\varphi_B & (x=1 \wedge y \neq 1) \vee (x=0 \wedge y \neq 0)
\end{array}\]
\begin{tabular}{l c}
\textsc{Yint} & $x-y=0$
\end{tabular}

@@

@@

As an Horn clause solver we incorporated our Horn clause solver to MoCHi.

\begin{figure}
\begin{center}
\includegraphics[scale=.6]{figures/unsat2.eps}
\quad
\includegraphics[scale=.6]{figures/unsat3.eps}
\end{center}
\caption{Result obtained from \textsc{MoCHi} with Horn clause solver \textsc{CSIsat} and
\textsc{Yhorn}}
\end{figure}

We obtained better result in some cases compared to the one we had in \textsc{CSIsat}.

>>>>

We implemented our proposed algorithm into \textsc{MoCHi} by two steps.  First,
we replace an existing theorem prover with our interpolating theorem
prover as a sub-routine for solving Horn clauses in dependent typing.
We used a method to obtain a common small interpolant across different
interpolating problems, while reducing a Horn clause problem into
interpolation \cite{conf/ppdp/UnnoK09}.  Second, we completely
replaced \textsc{MoCHi}'s Horn solving algorithm with our algorithm.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.1]{figures/int1.eps}
\end{center}
\caption{Complex problem 1}
\label{fig:int1}
\end{figure}

Finally, we showed some test cases that may occur in practical interpolation.
\begin{itemize}
\item Problem in Figure~\ref{fig:int1}
\[\begin{array}{r c}
\multirow{2}{*}{$\varphi_A$}
& ((x-y-1 \leq 0) \wedge (-x+y-2 \leq 0) \wedge (x+y-1 \leq 0) \wedge (-x-y-2 \leq 0)) \vee \\
& ((x-y-2 \leq 0) \wedge (-x+y-1 \leq 0) \wedge (x+y-2 \leq 0) \wedge (-x-y-1 \leq 0)) \\
\hline
\varphi_B : & (x=0 \wedge y=2) \vee (x=0 \wedge y=-2)
\end{array}\]
\[\begin{array}{l c}
\text{\textsc{Yint}} & (-x+17y-33 \leq 0) \wedge (x-17y-33 \leq 0) \\
\text{\textsc{CSIsat}} & ((-1 \leq (x + y) \vee (x + -y) \leq 1) \wedge (-1 \leq (x + -y) \vee (x + y) \leq 1))
\end{array}\]

\item Problem in Figure~\ref{fig:int2}
\[\begin{array}{r c}
\multirow{2}{*}{$\varphi_A$}
& ((y+1=0) \wedge (x-1=0)) \vee ((y+1=0) \wedge (x+1=0)) \vee \\
& ((y-1=0) \wedge (x+1=0)) \vee ((y-1=0) \wedge (x-1=0)) \\
\hline
\multirow{2}{*}{$\varphi_B$}
& ((y+2 \leq 0) \wedge (x-2 \geq 0)) \vee ((y+2 \leq 0) \wedge (x+2 \leq 0)) \vee \\
& ((y-2 \geq 0) \wedge (x+2 \leq 0)) \vee ((y-2 \geq 0) \wedge (x-2 \geq 0))
\end{array}\]
\begin{tabular}{l c}
\textsc{Yint} & $(-2y-3 \leq 0) \wedge (2y-3 \leq 0)$
\end{tabular}

@@

\item Problem in Figure~\ref{fig:int3}
\[\begin{array}{r c}
\varphi_A & (x=1 \wedge y=1) \vee (x=0 \wedge y=0) \\
\hline
\varphi_B & (x=1 \wedge y \neq 1) \vee (x=0 \wedge y \neq 0)
\end{array}\]
\begin{tabular}{l c}
\textsc{Yint} & $x-y=0$
\end{tabular}

@@

\end{itemize}

\begin{figure}[htb]
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=1.1]{figures/int2.eps}
  \caption{Complex problem 2}
  \label{fig:int2}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.47\textwidth}
  \centering
  \includegraphics[scale=1.1]{figures/int3.eps}
  \caption{Complex problem 3}
  \label{fig:int3}
  \end{minipage}
\end{figure}

@@

As an Horn clause solver we incorporated our Horn clause solver to
existing software model checker \textsc{MoCHi}.  It generates a Horn
clause solving problem while performing dependent type inference for
input program.

The previous \textsc{MoCHi} used Horn clause solving algorithm
proposed by Unno et al. \cite{conf/ppdp/UnnoK09}.  Its implementation
adopts \textsc{CSIsat} for solving interpolation problems that appear
as sub problems of Horn clause solving.

We configured \textsc{MoCHi} to use \textsc{TRecS} version 1.30 for
higher order model checking of abstract model of input programs.  The
experiments are performed for comparison between Unno's algorithm with
convex hull optimization in predicates (\texttt{-gchi} option) and our
algorithm (\texttt{-yhorn} option).  The test cases are available in
\textsc{MoCHi}'s development repository or online web interface.

For each test program, we compared the number of CEGAR cycles for
verification.  Additionally, for each Horn clause solving problem, we
inspected the quality of solutions.  The quality is evaluated by the
number of conjunctions and disjunctions in total.  Finally, we
compared the time consumed for solving each problem.
